Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-19 reviews/response.tex

  To better balance the exposition, we reorganized Chapter 4 of the previous version of the draft into two new chapters (now Ch.\ 4, entitled ``Exact Support Recovery Under Dependence'',  and Ch.\ 5 ``Bayes and Minimax Optimality''). 
  This change, in addition to making all chapters more manageable and of about equal lengths, exposes more clearly our contributions. 
  The results contained in Chapters 4 and 5 as well as the more probabilistic Chapter 6 and the more applied Chapter 7 are original contributions to the literature.

  Following the suggestion of R2,  we have placed most proofs in the text after the corresponding claims (theorems, propositions, lemmas).  In the interest of space and to conform with the format of the SpringerBriefs series, we no longer include ``Exercises'' sections.

  \item {\bf (Typos, grammar, and style)}  Prompted by the suggestions of R2, we have revised the language of the manuscript. 
  There have been extensive re-writes throughout the manuscript in order to make the content more connected and style more consistent.  
  In trying to make the text more accessible, we re-formatted the statements of most theorems to make them more modular. 
  We have also corrected typos and missing articles.

   \item {\bf (An improvement)} We implemented a small improvement, which broadens the scope of our exact support recovery results.  Specifically, we noticed that 
   the size of the signal support $|S_p|$  (previously $|S_p| = \lfloor p^{1-\beta}\rfloor$) can be parameterized as
   $$
   |S_p| \sim \ell(p)p^{1-\beta},\ \ \mbox{ as }p\to\infty, 
   $$
   where $0<\beta\le 1$ and where $\ell(\cdot)$ is a slowly varying function.  This more general parameterization required only minor, cosmetic changes to some
   proofs in Chapters 4 and 5.
